Precise Data Flow Analysis\\in the Presence of Correlated Method Calls

### 2015-03-09 sas2015/content/appendix.tex
ondrejs comments

\efficient*
\begin{proof}
\leavevmode
  \begin{enumerate}
    \item The identity function is represented as $\lambda r\,.\,\setpair{\bot_T}{\top_T}$. 
    The top function is represented as $\lambda r\,.\,\setpair{\top_T}{\top_T}$.
    \item Lemmas~\ref{lem:equalComp} and \ref{lem:equalMeet} show that the representation of micro functions is closed under composition and meet.
    \item To show that our representation for micro functions forms a lattice with finite height, let us first show that $\lcc_\rcc:\,\rcc\to2^T$ forms a lattice. Since $T$ is a finite set, $(2^T,\,\subseteq)$ is a finite-height lattice. $\rcc$ is a finite set. Hence, the mapping
    \[
      \rcc\mapsto2^T=\{(r,\,t)\,|\,r\in \rcc,\,t\in 2^T\}=\lcc_\rcc
    \]        
    also forms a finite-height lattice~\cite{nielson1999principles}.

>>>>

\subsubsection*{Efficiency}
We will next introduce the complexity proof for the correlated-calls algorithm.
To satisfy the complexity requirements of the IDE algorithm, we need to provide
an implementation of the IDE lattice and micro-functions that satisfy the following
list of criteria~\cite{sagiv1996precise}:
\begin{enumerate}
	\item There is a representation for the identity and top functions.
  \item The representation is closed under the meet and composition operations.
  \item The micro functions form a finite-height lattice.
  \item The apply, meet, composition, and equality-check operations can be computed in constant time (independent of $E$ and $D$).
  \item There is a constant bound on the storage space for a micro function representation.
\end{enumerate}
\efficient*
\begin{proof}
\leavevmode
  \begin{enumerate}
    \item The identity function is represented as $\lambda r\,.\,\setpair{\bot_T}{\top_T}$. 
    The top function is represented as $\lambda r\,.\,\setpair{\top_T}{\top_T}$.
    \item Lemmas~\ref{lem:equalComp} and \ref{lem:equalMeet} show that the representation of micro functions is closed under composition and meet.
    \item To show that our representation for micro functions forms a lattice with finite height, let us first show that $\lcc_\rcc:\,\rcc\to2^T$ forms a lattice. Since $T$ is a finite set, $(2^T,\,\subseteq)$ is a finite-height lattice. $\rcc$ is a finite set. Hence, the mapping
    \[
      \rcc\mapsto2^T=\{(r,\,t)\,|\,r\in \rcc,\,t\in 2^T\}=\lcc_\rcc
    \]        
    also forms a finite-height lattice~\cite{nielson1999principles}.

### 2015-03-09 sas2015/content/impl.tex
ondrejs comments

An IFDS solution $\resultIFDS$ has type $N^* \to D$: it maps each program point $n$
to a set of facts $d$ that may be reached at $n$.
\otodo{This seems wrong: Why is it $N^*$ for IFDS and $N$ for IDE? And shouldn't
    it be $N \to 2^D$, since you get a set of $d$'s?}
An IDE solution $\resultIDE$
pairs each such fact~$d$ with a lattice element $\ell$, so its type
is $N \to (D \to L)$.

>>>>

An IFDS solution $\resultIFDS$ has type $N^* \to 2^D$: it maps each program point $n$
to a set of facts $d$ that may be reached at $n$.
\otodo{This seems wrong: Why is it $N^*$ for IFDS and $N$ for IDE? And shouldn't
    it be $N \to 2^D$, since you get a set of $d$'s?}
An IDE solution $\resultIDE$
pairs each such fact~$d$ with a lattice element $\ell$, so its type
is $N^* \to (D \to L)$.
